An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Merge?

\newcommand{\isDraft}{true}

@@

\input{fig_dia_method_safety}

@@

\input{fig_dia_method_safety_by_refinement}

@@

\input{fig_dia_method_invariant}

@@

\input{fig_dia_method_invariant_w_minimization}

@@

\input{fig_dia_method_invariant_by_refinement}

>>>>

\newcommand{\isDraft}{false}

@@

\ifthenelse{\equal{\isDraft}{true}}{\input{fig_dia_method_safety}}{}

@@

\ifthenelse{\equal{\isDraft}{true}}{\input{fig_dia_method_safety_by_refinement}}{}

@@

\ifthenelse{\equal{\isDraft}{true}}{\input{fig_dia_method_invariant}}{}

@@

\ifthenelse{\equal{\isDraft}{true}}{\input{fig_dia_method_invariant_w_minimization}}{}

@@

\ifthenelse{\equal{\isDraft}{true}}{\input{fig_dia_method_invariant_by_refinement}}{}
